Lens Modeling in \sw

### 2013-09-08 text/tex/results.tex
ideas for outlook, errornames in gen_table
added eR plots
cleaned up make files

\begin{enumerate}
  \item innacurate placement in an extended arc
  \item wrongly identified sad and min in 3 image configuration
  \item identified only 3 instead of 5 images
  \item tried to model an arc with a min instead of min-sad-min
  \item PI-err (rotation by 180 degrees; in 5 image configuration, exchanged the ordering of the two saddle points)
  \item PI/2-err (rotation by 90 degree; sad->min->sad->min->sad)
  \item missed faint image(s)
  \item tried to model an arc with min-sad-min instead of only min
  \item did identify two close by images as one
  \item used 7 or more image to model a 5 image system.
\end{enumerate}

@@

>>>>

\begin{enumerate}
  \item inaccurate placement in an extended arc
  \item wrongly identified sad and min in 3 image configuration
  \item identified only 3 instead of 5 images
  \item tried to model an arc with a min instead of min-sad-min
  \item PI-err (rotation by 180 degrees; in 5 image configuration, exchanged the ordering of the two saddle points)
  \item PI/2-err (rotation by 90 degree; sad$\longmapsto$min$\longmapsto$sad$\longmapsto$min$\longmapsto$sad)
  \item missed faint image(s)
  \item tried to model an arc with min-sad-min instead of only min
  \item did identify two close by images as one
  \item used 7 or more image to model a 5 image system.
\end{enumerate}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/sims/eR_4.png}
  \caption{relative Einstein Radius for each model, per sim. }
  \label{fig:eR_all}
\end{figure}

\hr
